---
title: "cmqt_anthropometry_qc"
author: "Alyna Khan"
date: "2023-11-07"
output: html_document
---

# Description

This document performs quality control checks on the cmqt_anthropometry data sets. Specific checks are determined through a collaborative effort between the CMQT sub-working group, the Phenotype Harmonization Working Group, and the CC. 

# Quailty checks
## Libraries
```{r setup3, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(AnvilDataModels) #remotes::install_github("UW-GAC/AnvilDataModels")
library(AnVIL)
library(readr)
library(tidyverse)
library(dplyr)
library(knitr)
library(DT)
library(xtable)
```

## R Markdown

```{r hello3}
# Include table-specific QC checks
print("hello world!")
```

## Read in data
```{r read-in-data}
test_df <- read.table(file = '/home/rstudio/primed-file-checks/pheno_qc/test_data/cmqt_anthropometry.tsv', sep = '\t', header = TRUE)
```

## Variable-specific QC limits
```{r variable-specific-qc-limits}
# Set min and max extreme values for height, weight, bmi

vars <- c('height_1', 'weight_1', 'bmi_1')
min_values <- c(0, 0, 0) 
min_values <- as.list(setNames(min_values, vars))
max_values <- c(400, 300, 100)
max_values <- as.list(setNames(max_values, vars))
```

## Generate data set to run through QC checks 
```{r generate-test-data, include=FALSE}
# # Create data frame 
# num_samples_pass <- 50 
# num_samples_fail <- 10
# total_samples <- num_samples_pass + 2*num_samples_fail
# test_df <- data.frame(matrix(ncol = length(vars), nrow = total_samples))
# 
# # Provide column names
# colnames(test_df) <- vars
# 
# for(var_name in vars){
#   min <- min_values[[var_name]]
#   max <- max_values[[var_name]]
#   samples1 <- runif(num_samples_pass, min, max)
#   samples2 <- runif(num_samples_fail, min = min-10, max = min)
#   samples3 <- runif(num_samples_fail, min = max, max = max+100)
#   c <- c(samples1, samples2, samples3)
#   
#   # Put test data into dataframe
#   test_df[var_name] <- c
# }
# 
# # Change BMI to match calculation, keep some out of specified range
# test_df <- test_df %>% mutate (
#   bmi_1 = case_when(height_1 > max_values[['height_1']] ~ weight_1 / (height_1 / 100), 
#                     TRUE ~ weight_1 / (height_1 / 100)^2)
# )
```

## Variable-specific QC checks
```{r variable-specific-qc}
# Check for extreme values in dataset

this_table <- as.data.frame(test_df) # for testing 

print(head(this_table))

for (var_name in vars) {
  this_variable <- eval(parse(text=paste0("this_table$", var_name)))
  
  max <- max_values[[var_name]]
  min <- min_values[[var_name]]
  
  if(sum(this_variable > max) + sum(this_variable < min) > 0) {
    print(paste(sum(this_variable > max), ' samples with ', var_name, '>', max))
    print(paste(sum(this_variable < min), ' samples with ', var_name, '<', min))
  }
}

# Check for errors in BMI calculations 
this_table <- this_table %>% mutate(
  bmi_check = weight_1 / (height_1/100)^2
  )

if(sum(this_table$bmi_1 != this_table$bmi_check) > 0) {
    print(paste(sum(this_table$bmi_1 != this_table$bmi_check), ' samples with incorrect bmi calcation'))
  }
```
