---
title: "cmqt_hematology Quality Checks"
output:
  html_document:
    toc: true
    theme: united
    df_print: paged
date: `r format(Sys.time(), "%d %B, %Y")`
author: "Alyna Khan"
---

# Description
<Provide a description of table>

Example: This document performs quality control checks on the cmqt_hematology data sets. Specific checks are determined through a collaborative effort between the CMQT sub-working group, the Phenotype Harmonization Working Group, and the CC. 

# Quailty checks
## Libraries
```{r load-libraries}
# Will not need this code chunk when this is integrated into main_qc markdown doc
```

## Read in data
```{r read-in-data}

```

## Variable-specific QC limits
```{r variable-specific-qc-limits}
# Set biologically implausible values for blood pressure

vars <- c('wbc_1', 'hemoglobin_1', 'hematocrit_1', 'platelet_count_1')
min_values <- c(0, 0, 0, 0) 
min_values <- as.list(setNames(min_values, vars))
max_values <- c(200, 20, 60, 1000)
max_values <- as.list(setNames(max_values, vars))
```

## Generate data set to run through QC checks 
```{r generate-test-data}
# Create data frame 
num_samples_pass <- 50 
num_samples_fail <- 10
total_samples <- num_samples_pass + 2*num_samples_fail
test_df <- data.frame(matrix(ncol = length(vars), nrow = total_samples))

# Provide column names
colnames(test_df) <- vars

for(var_name in vars){
  min <- min_values[[var_name]]
  max <- max_values[[var_name]]
  samples1 <- runif(num_samples_pass, min, max)
  samples2 <- runif(num_samples_fail, min = min-10, max = min)
  samples3 <- runif(num_samples_fail, min = max, max = max+100)
  c <- c(samples1, samples2, samples3)
  
  # Put test data into dataframe
  test_df[var_name] <- c
}
```

## Variable-specific QC checks
```{r variable-specific-qc}
# Check for extreme values in dataset

this_table <- as.data.frame(test_df) # for testing

for (var_name in vars) {
  this_variable <- eval(parse(text=paste0("this_table$", var_name)))
  
  max <- max_values[[var_name]]
  min <- min_values[[var_name]]
  
  if(sum(this_variable > max) + sum(this_variable < min) > 0) {
    print(paste(sum(this_variable > max), ' samples with ', var_name, '>', max))
    print(paste(sum(this_variable < min), ' samples with ', var_name, '<', min))
  }
}
```
