
```{r}
# check file_name and df passed in 

# head(df)
# print(file_name)
```

```{r}
# Check for errors in BMI calculations 

bmi_tolerance <- 0.1 

this_table <- df %>% mutate(
  bmi_calculated = weight_1 / (height_1/100)^2,
  bmi_diff = bmi_1 - bmi_calculated
  )

vars_df <- data.frame(c("bmi_consistency"))
vars_df$min <- round(min(this_table$bmi_1 - this_table$bmi_calculated, na.rm=TRUE), 2)
vars_df$max <- round(max(this_table$bmi_1 - this_table$bmi_calculated, na.rm=TRUE), 2)
vars_df$mean <- round(mean(this_table$bmi_1 - this_table$bmi_calculated, na.rm=TRUE), 2)
vars_df$median <- round(median(this_table$bmi_1 - this_table$bmi_calculated, na.rm=TRUE), 2)
vars_df$qc_min <- bmi_tolerance * -1
vars_df$qc_max <- bmi_tolerance * 1
vars_df$qc_pass <- sum(
    this_table$bmi_1 >= this_table$bmi_calculated - bmi_tolerance
    & this_table$bmi_1 <= this_table$bmi_calculated + bmi_tolerance, 
    na.rm=TRUE
    )
vars_df$qc_fail_min <- c(sum(this_table$bmi_1 < this_table$bmi_calculated - bmi_tolerance, na.rm=TRUE))
vars_df$qc_fail_max <- c(sum(this_table$bmi_1 > this_table$bmi_calculated + bmi_tolerance, na.rm=TRUE))
vars_df$qc_null <- c(sum(is.na(this_table$bmi_calculated)))
```

CMQT Anthropometry Specific Variables: 

- bmi_consistency: Difference between reported BMI and calculated BMI (reported - calculated)
  - QC Min: NA
  - QC Max: NA
  - Pass QC: number of samples with reported BMI within a tolerance level of 0.1 of calculated BMI
  - Fail QC Min: number of samples with reported BMI difference less than (calculated BMI - 0.1)
  - Fail QC Max: number of samples with reported BMI difference greater than (calculated BMI + 0.1)
  - Null Values: number of samples with null values for height_1 or weight_1

```{r}
kable(vars_df, col.names = c('Variable', 'Min Value', 'Max Value', "Mean", "Median", "QC Min", "QC Max", 'Pass QC', 'Fail QC Min', 'Fail QC Max', 'Null Values'))
```

```{r}
ggplot(aes(x=bmi_diff), data=this_table) +
  geom_histogram(bins = 15) +
  xlab("Difference between reported BMI and calculated BMI")
```