
```{r}
# check file_name and df passed in 

# head(df)
# print(file_name)

# file_name <- 'gs://fc-secure-0285a1eb-c88a-4ea6-b970-ec5e092784ea/uploaded_data_prevent/aric_cmqt_anthropometry.tsv'
# table_pipe <- gsutil_pipe(file_name, "rb")
# df <- read_table(table_pipe, 
#                  col_types = cols(subject_id="c"), 
#                  guess_max=Inf, 
#                  show_col_types=TRUE)
```

```{r}
# Check for errors in BMI calculations 

bmi_tolerance <- 0.1

this_table <- this_table %>% mutate(
  bmi_calculated = weight_1 / (height_1/100)^2,
  bmi_diff = bmi_1 - bmi_calculated
  )

vars_df <- vars_df %>% add_row(
  vars = 'bmi_consistency',
  min = min(this_table$bmi_calculated - bmi_tolerance, na.rm=TRUE), 
  max = max(this_table$bmi_calculated - bmi_tolerance, na.rm=TRUE), 
  mean = mean(this_table$bmi_calculated - bmi_tolerance, na.rm=TRUE), 
  median = median(this_table$bmi_calculated - bmi_tolerance, na.rm=TRUE), 
  qc_min = bmi_tolerance * -1,
  qc_max = bmi_tolerance * 1,
  qc_pass = sum(
    this_table$bmi_1 >= this_table$bmi_calculated - bmi_tolerance
    & this_table$bmi_1 <= this_table$bmi_calculated + bmi_tolerance, 
    na.rm=TRUE
    ),
  qc_fail_min = c(sum(this_table$bmi_1 < this_table$bmi_calculated - bmi_tolerance, na.rm=TRUE)),
  qc_fail_max = c(sum(this_table$bmi_1 > this_table$bmi_calculated + bmi_tolerance, na.rm=TRUE)),
  qc_null = c(sum(is.na(this_table$bmi_calculated)))
)
```

General Variables: 

- age: 
  - QC Min: 0
  - QC Max: 90
- r vars
  - QC Min: -4SD outlier
  - QC Min: +4SD outlier

CMQT Anthropometry Specific Variables: 

- bmi_consistency: Difference between reported BMI and calculated BMI
  - QC Min: NA
  - QC Max: NA
  - Pass QC: number of samples with reported BMI within a tolerance level of 0.1 of calculated BMI
  - Fail QC Min: number of samples with reported BMI difference less than (calculated BMI - 0.1)
  - Fail QC Max: number of samples with reported BMI difference greater than (calculated BMI + 0.1)
  - Null Values: number of samples with null values for height_1 or weight_1

```{r}
kable(rbind(age_df, vars_df), col.names = c('Variable', 'Min Value', 'Max Value', "Mean", "Median", "QC Min", "QC Max", 'Pass QC', 'Fail QC Min', 'Fail QC Max', 'Null Values'))
```

```{r}
ggplot(aes(x=bmi_diff), data=this_table) +
  geom_histogram() +
  xlab("Difference between reported BMI and calculated BMI")
```