
```{r}
# check file_name and df passed in 

# head(df)
# print(file_name)

# file_name <- 'gs://fc-secure-0285a1eb-c88a-4ea6-b970-ec5e092784ea/uploaded_data_prevent/aric_cmqt_anthropometry.tsv'
# table_pipe <- gsutil_pipe(file_name, "rb")
# df <- read_table(table_pipe, 
#                  col_types = cols(subject_id="c"), 
#                  guess_max=Inf, 
#                  show_col_types=TRUE)
```

```{r}
# Set min and max limits for QC check 

vars <- c('height_1', 'weight_1', 'bmi_1')

# min and max values that are biologically implausible 
# min_values <- c(0, 0, 0)
# max_values <- c(400, 300, 100)

# min and max values that are mean +/- 4 SD outlier detection
min_values <- apply(df[vars], 2, mean, na.rm=TRUE) - 4*apply(df[vars], 2, sd, na.rm=TRUE)
max_values <- apply(df[vars], 2, mean, na.rm=TRUE) + 4*apply(df[vars], 2, sd, na.rm=TRUE)

vars_df <- data.frame(vars)
vars_df$min_values <- min_values
vars_df$max_values <- max_values
vars_df$qc_pass <- c(rep(-1, length(vars)))
vars_df$qc_fail_min <- c(rep(-1, length(vars)))
vars_df$qc_fail_max <- c(rep(-1, length(vars)))
vars_df$qc_null <- c(rep(-1, length(vars)))
```

```{r}
# Check for extreme values in dataset
this_table <- as.data.frame(df) 

for (i in 1:length(vars)) {
  var_name = vars[i]
  
  this_variable <- eval(parse(text=paste0("this_table$", var_name)))
  
  max <- vars_df[i, 3]
  min <- vars_df[i, 2]
  
  vars_df[c(i),]$qc_pass <- c(sum(this_variable <= max & this_variable >= min, na.rm=TRUE))
  vars_df[c(i),]$qc_fail_min <- c(sum(this_variable < min, na.rm=TRUE))
  vars_df[c(i),]$qc_fail_max <- c(sum(this_variable > max, na.rm=TRUE))
  vars_df[c(i),]$qc_null <- c(sum(is.na(this_variable)))
}

# Check for errors in BMI calculations 

bmi_tolerance <- 0.1

this_table <- this_table %>% mutate(
  # bmi_calculated = ifelse(!is.na(weight_1) & !is.na(height_1), weight_1 / (height_1/100)^2, NULL),
  bmi_calculated = weight_1 / (height_1/100)^2,
  bmi_diff = bmi_1 - bmi_calculated
  )

vars_df <- vars_df %>% add_row(
  vars = 'bmi_consistency',
  min_values = bmi_tolerance * -1,
  max_values = bmi_tolerance * 1,
  qc_pass = sum(
    this_table$bmi_1 >= this_table$bmi_calculated - bmi_tolerance
    & this_table$bmi_1 <= this_table$bmi_calculated + bmi_tolerance, 
    na.rm=TRUE
    ),
  qc_fail_min = c(sum(this_table$bmi_1 < this_table$bmi_calculated - bmi_tolerance, na.rm=TRUE)),
  qc_fail_max = c(sum(this_table$bmi_1 > this_table$bmi_calculated + bmi_tolerance, na.rm=TRUE)),
  qc_null = c(sum(is.na(this_table$bmi_calculated)))
)
```

CMQT Anthropometry Specific Variables checked: 

- height_1
  - Min Value: -4SD outlier
  - Min Value: +4SD outlier
- weight_1
  - Min Value: -4SD outlier
  - Min Value: +4SD outlier
- bmi_1
  - Min Value: -4SD outlier
  - Min Value: +4SD outlier
- bmi_consistency: Difference between reported BMI and calculated BMI
  - Min Value: NA
  - Min Value: NA
  - Pass QC: number of samples with reported BMI within a tolerance level of 0.1 of calculated BMI
  - Fail QC Min: number of samples with reported BMI difference less than (calculated BMI - 0.1)
  - Fail QC Max: number of samples with reported BMI difference greater than (calculated BMI + 0.1)
  - Null Values: number of samples with null values for height_1 or weight_1

```{r}
kable(vars_df, col.names = c('Variable', 'Min Value', 'Max Value', 'Pass QC', 'Fail QC Min', 'Fail QC Max', 'Null Values'),  caption = "QC check for anthropometry variables")
```

```{r}
ggplot(aes(x=bmi_diff), data=this_table) +
  geom_histogram() +
  xlab("Difference between reported BMI and calculated BMI")
```