---
title: Adding your phenotype data file to the harmonized data table
author: Alyna Khan
date: 
---
# Elements needed to prepare your harmonized data table
Both harmonized and unharmonized phenotype data tables can be imported into your AnVIL workspace. To import harmonized data, you must create a harmonized data table. There are 6 elements needed to prepare your harmonized data table:
* domain: refers to the phenotype domain that your harmonized data file belongs to (e.g., cvd_cad)
* md5sum: refers to the md5sum value associated with your data file
* file_path: refers to the google bucket ID of your harmonized data file
* file_readme_path: refers to the google bucket ID of your README file
* n_subjects: refers to the number of subjects in your phenotype data file
* n_rows: refers to the number of rows in your phenotype data file. Do not count the header as a row.

# Install and load R packages
```{r libraries}
#remotes::install_github("UW-GAC/AnvilDataModels", upgrade=FALSE)
library(AnVIL)
library(AnvilDataModels)
library(tidyverse)
```

# Prepare your harmonized data table
To access files in the source workspace, you will need the source workspace google bucket ID. With the ID, you can list all the files in your source workspace.
```{r get_buckets}
# Get your source google bucket ID
bucket <- "gs://fc-995e5705-8dcb-410b-987e-c05b47d0c580"

# List the files in your source bucket
gsutil_ls(bucket)

# Get the google bucket ID for your data file
prefix_cad_data <- "cvd_cad"
cad_data_file <- paste0(bucket, "/", prefix_cad_data, ".txt")

# Check that the bucket ID for your data file is in your source bucket file list
cad_data_file %in% gsutil_ls(bucket)
```

Get the bucket ID for the harmonized data table.
```{r read_data}
bucket <-"gs://fc-995e5705-8dcb-410b-987e-c05b47d0c580" # In this case, source_bucket and harmonized table bucket are the same
prefix <- "TEST_harmonized_phenotype_table"
harmonized_table_file <- paste0(bucket, "/", prefix, ".tsv")
harmonized_table_file %in% gsutil_ls(bucket)
harmonized_table_pipe <- gsutil_pipe(harmonized_table_file, "rb")
harmonized_table <- read_table(harmonized_table_pipe)
```

```{r add-pheno-file}
# Add a row for the new phenotype data file
harmonized_table_added_file <- add_row(harmonized_table, domain="cvd_cad", file_path=cad_data_file, file_readme_path = "readme", n_subjects=7, n_rows=7, md5sum="1fa255d535cf40fc1e8d4a55155a6657")
```

# Write tables as files to workspace bucket
Add your harmonized table to the workspace using the workspace bucket ID
```{r create-table-file}
outfile <- "TEST_harmonized_phenotype_table_4.tsv"
write_tsv(harmonized_table_added_file, outfile)
gsutil_cp(outfile, bucket)
```

# Check tables against data model
Once you've added your phenotype harmonized data table, you can run the validation workflow to check the table against the data model. 