---
title: "Quality Checks on PRIMED Phenotype Data"
author: "Alyna Khan"
output:
  html_document:
    df_print: paged
---

The phenotype quality check (QC) workflow performs basic data QC on harmonized phenotype data in PRIMED. The checks conducted in the workflow were approved by the Phenotype Harmonization Working Group and the phenotype domain sub-working groups. Phenotype data is heterogeneous, and expected QC results may be context-specific based on a number of factors, including phenotype definition, data variable type, study sample, etc. Therefore, these checks only provide a broad view of the data to help identify any glaring issues. More detailed QC checks should be performed by the analyst to ensure appropriate quality control. 

## Load packages
```{r libraries, echo=FALSE}
library(AnvilDataModels) # remotes::install_github("UW-GAC/AnvilDataModels")
library(AnVIL)
library(readr)
library(tidyverse)
library(dplyr)
library(knitr)
library(DT)
library(xtable)
```

## Read in data

```{r test-aric-anthropometry}
# Get your source google bucket ID
bucket <- "gs://fc-secure-0285a1eb-c88a-4ea6-b970-ec5e092784ea/uploaded_data_prevent"

# Get the google bucket ID for your data file
prefix_anthro_data <- "aric_cmqt_anthropometry"
anthro_data_file <- paste0(bucket, "/", prefix_anthro_data, ".tsv")

# Check that the bucket ID for your data file is in your source bucket file list
anthro_data_file %in% gsutil_ls(bucket)

# Read in dataset
anthro_table_pipe <- gsutil_pipe(anthro_data_file, "rb")
anthro_dataset <- read_table(anthro_table_pipe)
dat <- anthro_dataset
```

## Generate data summaries: Sample size and age
```{r qc-file, echo=FALSE}
# Get dataset
this_table <- as.data.frame(dat)
vars_to_qc <- names(this_table)[which(!names(this_table) %in% c("subject_id", "visit", "age_at_obs"))]

# Get min and max values (currently using placeholder min and max values specific to columns in anthro dataset)
min_values <- c(0, 0, 0) 
min_values <- as.list(setNames(min_values, vars_to_qc))
max_values <- c(400, 300, 100)
max_values <- as.list(setNames(max_values, vars_to_qc))

# Get sample size and unique sample size
sample_size <- length(this_table$subject_id)
unique_samples <- length(unique(this_table$subject_id))

# Get age distribution
age_summary <- summary(this_table$age_at_obs)

# Check that age values fall within 0 and 89
age_over_max <- sum(this_table$age_at_obs > 89)
age_under_min <- sum(this_table$age_at_obs < 0)

age_p <- ggplot(this_table, aes(x=age_at_obs)) + 
  geom_histogram() + 
  #geom_density(alpha=0.25) +
  labs(title="Age distribution", x="Age")

# Print output
print(vars_to_qc) # print variables included in this data file
print(sample_size) # print sample size of data file
print(unique_samples) # print number of unique samples in data file
print(age_summary) # print summary stats for age variable
print(age_p) # print distribution of age variables

if(age_over_max + age_under_min > 0) {
  print(age_under_min, ' samples with age < 0')
  print(age_over_max, ' samples with age > 89')
} else {
  print('All age values within 0 to 89')
}
```

## Generate summaries and plots of each variable
```{r qc-variable-2, echo=FALSE}
this_table <- as.data.frame(test_df)

for(var_name in vars_to_qc){
  this_variable <- eval(parse(text=paste0("this_table$", var_name)))
  
  # QC for numeric variable types
  if(is.numeric(this_variable)){
    
    if(all(this_variable %in% c(0,1)) == FALSE){ # QC checks for continuous variables
      
      # Get variable summary: min, max, mean, median 
      this_variable_summary <- summary(this_variable)
      
      # ADD MORE QC CHECKS HERE ########################################
      
      # check for values out of min and max
      max <- max_values[[var_name]]
      min <- min_values[[var_name]]
      if(sum(this_variable > max) + sum(var_name < min) > 0) {
        print(cat(sum(this_variable > max), ' samples with ', var_name, '>', max))
        print(cat(sum(this_variable < min), ' samples with ', var_name, '<', min))
      }
      
    
    # Plot continuous variable
    p <- ggplot(this_table, aes(x=this_variable)) + 
      geom_histogram(color="darkgray", fill="darkgray") + 
      xlab(var_name) +
      labs(title=paste0("Distribution of ", var_name))
    
    }else{ # QC checks for binary variables (0/1)
      
      # Make table of counts 
      this_variable_summary <- table(as.character(this_variable))
      
      # ADD MORE QC CHECKS FOR BINARY VARIABLES HERE ####################
      
      
      
      
      # Plot binary variable
      p <- ggplot(this_table, aes(x=as.character(this_variable))) + 
      geom_bar() + 
      xlab(var_name) + ylab("Count") + 
      labs(title=paste0("Count of ", var_name))
      
    }
    
    # QC checks for categorical variable data type
  } else if(is.character(this_variable)){ 
    
      # Get counts of categorical variable values 
      this_variable_summary <- table(this_variable)
      
      # ADD MORE QC CHECKS FOR CATEGORICAL VARIABLES ####################
      
      
      
      
      # Plot categorical variable
      p <- ggplot(this_table) + 
        geom_bar(aes(x=this_variable), fill = "gray") + 
        xlab(var_name) + ylab("Count") + 
        labs(title=paste0("Count of ", var_name))
      
  }
  
  print(p) # print distribution of variable
  print(this_variable_summary) # print summary stats of variable
     
}
```

## Generate data set to run through QC checks 
```{r}
# create data frame 
num_samples_pass <- 50 
num_samples_fail <- 10
total_samples <- num_samples_pass + 2*num_samples_fail
test_df <- data.frame(matrix(ncol = length(vars_to_qc), nrow = total_samples))

#provide column names
colnames(test_df) <- vars_to_qc

for(var_name in vars_to_qc){
  min <- min_values[[var_name]]
  max <- max_values[[var_name]]
  samples1 <- runif(num_samples_pass, min, max)
  samples2 <- runif(num_samples_fail, min = min-10, max = min)
  samples3 <- runif(num_samples_fail, min = max, max = max+10)
  c <- c(samples1, samples2, samples3)
  
  # put random data into test dataframe
  test_df[var_name] <- c
}

test_df
```

