---
title: "Update workspace"
output: html_notebook
---

This notebook moves data from an update workspace to an original workspace.

Load R libraries

```{r}
library(AnVIL)
library(dplyr)
library(readr)
```

Define workspaces and input table files (copied from validation workflow input)

```{r}
original_bucket <- avbucket(namespace = "primed-cc-scratch", 
                            name = "PRIMED_example_genotype_1000G_test")
update_bucket <- avbucket(namespace = "primed-cc-scratch", 
                            name = "PRIMED_example_genotype_1000G_test_UPDATE")
validation_inputs_json <- '{ "sample_set": "gs://fc-7e3a3249-398c-43e9-baf0-1ab8a79bfd15/HapMap_sample_set.tsv", "array_dataset": "gs://fc-7e3a3249-398c-43e9-baf0-1ab8a79bfd15/HapMap_array_dataset.tsv", "array_file": "gs://fc-7e3a3249-398c-43e9-baf0-1ab8a79bfd15/HapMap_array_file.tsv" }'
```


Create new data tables and get vector of files to move

```{r}
validation_inputs_list <- jsonlite::fromJSON(validation_inputs_json)

files_to_move <- list()
new_validation_inputs <- list()

for (table in names(validation_inputs_list)) {
  input_path <- validation_inputs_list[[table]]
  table_file <- basename(input_path)
  gsutil_cp(input_path, table_file)
  dat <- read_tsv(table_file, col_types=cols(.default=col_character()))
  
  # get list of files to move
  files_to_move[[table]] <- lapply(dat, function(c) c[grep(update_bucket, c)]) %>%
    unlist() %>%
    unique()

  # update file paths in data tables
  dat <- dat %>%
    mutate_all(function(c) sub(update_bucket, original_bucket, c))
  write_tsv(dat, table_file)
  out_path <- file.path(original_bucket, "update_workspace_data_tables", table_file)
  gsutil_cp(table_file, out_path)
  new_validation_inputs[[table]] <- out_path
}

files_to_move <- unique(unlist(files_to_move))
```

Copy files

```{r}
# do this one file at a time to preserve full path
for (f in files_to_move) {
  gsutil_cp(f, sub(update_bucket, original_bucket, f))
}
```

Delete files from update workspace

```{r}
for (f in files_to_move) {
  gsutil_rm(f)
}
```

Create inputs for validation workflow with new data tables

```{r}
jsonlite::toJSON(new_validation_inputs, auto_unbox=TRUE, unbox=TRUE)
```

Run validation workflow

Copy notebook and submission directories

```{r}
gsutil_cp(paste0(update_bucket, "/notebooks/*"), paste0(original_bucket, "/notebooks/"), recursive=TRUE)
gsutil_cp(paste0(update_bucket, "/submissions/*"), paste0(original_bucket, "/submissions/"), recursive=TRUE)
```
